Deep Learning

### 2015-09-23 deepreview.tex
final small changes

% preview of deep learning results
Deep learning is making major advances in solving problems that have
resisted the best attempts of the Artificial Intelligence community
for many years. It has turned out to be very good at discovering
intricate structures in high-dimensional data and is therefore
applicable to many domains of science, business, and government. In
addition to beating records in image
recognition~\citep{Krizhevsky-2012-small,farabet-pami-13,tompson-nips-14,szegedy-2014}
and speech
recognition~\citep{Mikolov-ASRU-2011,Hinton-et-al-2012,Sainath-et-al-ICASSP2013}, it has
beaten other ML techniques at predicting the activity of potential
drug molecules~\citep{Ma-et-al-2015}, detecting new fundamental
particles~\citep{Ciodaro-et-al-2012,Melis-Higgs-boson-competition-2014},
% YB thinks that Ciodaro-et-al might be {YANNparticles} 
% classifying galaxies, ~\citep{YANNgalaxies}, % YB while waiting for bib entry, 
reconstructing brain circuits~\citep{helmstaedter-nature-2013}, and
predicting the effects of mutations in non-coding DNA on gene
expression and disease~\citep{Keung-et-al-2014,Xiong-et-al-Frey-science2015}.
Perhaps more surprisingly, deep learning has produced extremely
promising results for a variety of tasks in natural language
understanding~\citep{collobert:2011b}, particularly topic
classification, %~\citep{topic-classification},  % YB while waiting for bib entry
sentiment
analysis~\citep{Glorot+al-ICML-2011-small}, 
question-answering~\cite{Bordes-et-al-EMNLP2014}, and language
translation~\cite{Jean-et-al-arxiv2014,Sutskever-et-al-NIPS2014}.

@@

% deep neural nets
Many applications of deep learning use feedforward neural network
architectures, illustrated in Figure~\ref{fig:backprop-box}, which
learn to map a fixed-size input ({\it e.g.} an image) to a fixed-size
output ({\it e.g.} a probability for each of several categories). To
go from one layer to the next, a set of units compute a weighted sum
of their inputs from the previous layer and pass the result through a
non-linear function. Currently, the most popular non-linear function
is the rectified linear unit ({\em ReLU}) which is simply
the half-wave rectifier $f(z) = \max(z,0)$. In past decades, neural
nets used smoother non-linearities, such as $\tanh(z)$ or
$1/(1+\exp(-z))$ but the ReLU typically learns much faster in networks
with many layers. Units that are not in the input or output layer are
traditionally called {\em hidden units}. The hidden layers can be seen
as distorting the input in a non-linear way so that categories become
linearly separable by the last layer, as indicated in
figure~\ref{fig:backprop-box}.

>>>>

% preview of deep learning results
Deep learning is making major advances in solving problems that have
resisted the best attempts of the Artificial Intelligence community
for many years. It has turned out to be very good at discovering
intricate structures in high-dimensional data and is therefore
applicable to many domains of science, business, and government. In
addition to beating records in image
recognition~\citep{Krizhevsky-2012-small,farabet-pami-13,tompson-nips-14,szegedy-2014}
and speech
recognition~\citep{Mikolov-ASRU-2011,Hinton-et-al-2012,Sainath-et-al-ICASSP2013}, it has
beaten other ML techniques at predicting the activity of potential
drug molecules~\citep{Ma-et-al-2015}, detecting new fundamental
particles~\citep{Ciodaro-et-al-2012,Melis-Higgs-boson-competition-2014},
% YB thinks that Ciodaro-et-al might be {YANNparticles} 
% classifying galaxies, ~\citep{YANNgalaxies}, % YB while waiting for bib entry, 
reconstructing brain circuits~\citep{helmstaedter-nature-2013}, and
predicting the effects of mutations in non-coding DNA on gene
expression and disease~\citep{Keung-et-al-2014,Xiong-et-al-Frey-science2015}.
Perhaps more surprisingly, deep learning has produced extremely
promising results for a variety of tasks in natural language
understanding~\citep{collobert:2011b}, particularly topic
classification, %~\citep{topic-classification},  % YB while waiting for bib entry
sentiment
analysis,% cutting citations ~\citep{Glorot+al-ICML-2011-small}, 
question-answering~\cite{Bordes-et-al-EMNLP2014}, and language
translation~\cite{Jean-et-al-ACL2015,Sutskever-et-al-NIPS2014}.

@@

% deep neural nets
Many applications of deep learning use feedforward neural network
architectures, illustrated in Figure~\ref{fig:backprop-box}, which
learn to map a fixed-size input ({\it e.g.} an image) to a fixed-size
output ({\it e.g.} a probability for each of several categories). To
go from one layer to the next, a set of units compute a weighted sum
of their inputs from the previous layer and pass the result through a
non-linear function. Currently, the most popular non-linear function
is the rectified linear unit ({\em ReLU}) which is simply
the half-wave rectifier $f(z) = \max(z,0)$. In past decades, neural
nets used smoother non-linearities, such as $\tanh(z)$ or
$1/(1+\exp(-z))$ but the ReLU typically learns much faster in networks
with many layers, allowing to train a deep supervised network
without unsupervised pre-training~\citep{Glorot+al-AI-2011-small}. 
Units that are not in the input or output layer are
traditionally called {\em hidden units}. The hidden layers can be seen
as distorting the input in a non-linear way so that categories become
linearly separable by the last layer, as indicated in
figure~\ref{fig:backprop-box}.
